Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-12-01 paper/main.tex
new intro to intro math section

\section{Algebraic Topology And Category Theory}

>>>>

\section{Algebraic Topology And Category Theory}
Category theory can be used to express software specifications because it provides a method of expressing structure and how that structure can be composed \cite{wielsManagementEvolvingSpecifications1998} algebraic topology provides a rich language for expressing data continuity. In this section, we introduce concepts from algebraic topology and category theory that we will use in \autoref{sec:artist:category} to develop a formal model of specifying visualization component.
